|

### 2023-12-11 paper/paper.qmd
Add theme_minimal to some b/w plots

  ggplot(predictions) +
    geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),
                  width = 0.1,
                  colour = "orange") +
    geom_point(aes(x = x, y = predicted), colour = "black") +
    geom_text(aes(x = x, y = predicted, label = label),
              nudge_x = 0.25,
              size = 4) +
    scale_y_continuous(labels = scales::percent) +
    labs(y = "Kans op gij bent", x = "Dialectgebied")
}
```

@@

```{r}
bent_ratio_plot <- function() {
  ggplot(distribution, aes(x = bent_ratio)) +
  geom_histogram(bins=10) +
  facet_wrap( ~ dialect) +
  labs(y= "Aantal attestaties", x = "bent-ratio")
}
```

>>>>

  ggplot(predictions) +
    geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),
                  width = 0.1,
                  colour = "black") +
    geom_point(aes(x = x, y = predicted), colour = "black") +
    geom_text(aes(x = x, y = predicted, label = label),
              nudge_x = 0.25,
              size = 4) +
    scale_y_continuous(labels = scales::percent) +
    labs(y = "Kans op gij bent", x = "Dialectgebied") +
    theme_minimal()
}
```

@@

```{r}
bent_ratio_plot <- function() {
  ggplot(distribution, aes(x = bent_ratio)) +
  geom_histogram(bins=10) +
  facet_wrap( ~ dialect) +
  labs(y= "Aantal attestaties", x = "bent-ratio") +
  theme_minimal()
}
```
